### 2021-02-25 text/draft.tex
spread of keywords

\begin{figure}
\centering
\includegraphics{images/keywords_clean_histogram_abc.pdf}
\caption{In \texttt{keywords/keywords\_clean\_histogram.json}, the
distribution of keywords is strongly skewed right
(\(min = Q1 = M = Q3 = 1\) and \(max = 910\)). However, even though
keywords with only one occurrence constitute over 75\% of the total
keywords, their occurrences constitute less than 35\% of the total
occurrences. The most common keywords with 50 or more occurrences are
extreme outliers but make up almost 20\% of the total occurrences.}
\end{figure}

@@

There were X automatic matches (call them ``suggestions''). A suggestion
is correct if and only if the meaning of the keyword from
\texttt{/keywords/keywords\_clean\_histogram.json} corresponds to the
meaning of the suggested concept from Wikidata. Note that for homonymous
or polysemous keywords, it is impossible to confirm a correct match
without further context; those keywords therefore cannot be reconciled
(but see \protect\hyperlink{construction}{section ``Construction''} for
a possible solution). Unfortunately, random sampling showed that the
overall quality of the reconciliation was not satisfactory, that is,
there were too many incorrect suggestions. A two-pronged strategy was
adopted to ameliorate the quality of the reconciliation.

@@

@@

!! How many author keywords per item? !! How many suggestions per item
are correct?

@@

Or put as question: what fraction of the subject terms suggested by
Annif are also in the native gold standard?

@@

Put as question: what fraction of the subject terms in the gold standard
were suggested by Annif?

@@

!! number of keywords per item; number of keywords with qid per item

!! how to deal with items that have more than 10 keywords in standard??

@@

>>>>

\begin{figure}
\centering
\includegraphics{images/keywords_clean_histogram_abc.pdf}
\caption{In \texttt{keywords/keywords\_clean\_histogram.json}, the
distribution of keywords is strongly skewed right
(\(min = Q1 = M = Q3 = 1\), \(max = 910\)). However, even though
keywords with only one occurrence constitute over 75\% of the total
keywords, their occurrences constitute less than 35\% of the total
occurrences. The most common keywords with 50 or more occurrences are
extreme outliers but make up almost 20\% of the total occurrences.}
\end{figure}

To analyse the spread of keywords in the sample data set, the keywords
per item are counted. To do so, we call \texttt{\_Keywords.count\_all}
on \texttt{/indexed/indexed\_master\_mesh\_enriched.json} and save the
output as \texttt{/analysis/keywords\_counted.json}:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{sample\_data\_set }\OperatorTok{=}\NormalTok{ \_Utility.load\_json(DIR }\OperatorTok{+} \StringTok{"/indexed/indexed\_master\_mesh\_enriched.json"}\NormalTok{)}
\NormalTok{keywords\_counted }\OperatorTok{=}\NormalTok{ \_Keywords.count\_all(sample\_data\_set)}
\NormalTok{\_Utility.save\_json(keywords\_counted, DIR }\OperatorTok{+} \StringTok{"/analysis/keywords\_counted.json"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

The median number of keywords for an item in the sample data set is 6
with an \(IQR\) of 4 (\(min = 0\), \(Q1 = 4\), \(M = 6\), \(Q3 = 8\),
\(max = 87\)). Of course, items in the sample data set with a number of
keywords below the first and above the third quartile are highly suspect
from a qualitative point of view: when it comes to subject indexing,
some terms are required, but more is usually worse {[}!! source{]}.
Items with too few or too many keywords will be discussed in more detail
in section \protect\hyperlink{assessment}{section Assessment}

@@

The reconciliation service API returns automatic matches (call them
``suggestions''). A suggestion is correct if and only if the meaning of
the keyword from \texttt{/keywords/keywords\_clean\_histogram.json}
corresponds to the meaning of the suggested concept from Wikidata. Note
that for homonymous or polysemous keywords, it is impossible to confirm
a correct match without further context; those keywords therefore cannot
be reconciled (but see \protect\hyperlink{construction}{section
``Construction''} for a possible solution). Unfortunately, random
sampling showed that the overall quality of the reconciliation was not
satisfactory, that is, there were too many incorrect suggestions. A
two-pronged strategy was adopted to ameliorate the quality of the
reconciliation.

@@

Finally, consider the distribution of the cleaned and reconciled
keywords per item in the Edoc sample data set. The corresponding data is
generated with \texttt{\_Keywords.count\_all} as described in
\protect\hyperlink{analysis}{subsection Analysis} above and available as
\texttt{/analysis/keywords\_counted.json}. Figure 5 shows that the
median number of keywords from MeSH or YSO might be too low to be
adequate. This problem can be amended by imposing further constraints on
the sample data set and such a solution is discussed in section {[}!!
section{]}.

\begin{figure}
\centering
\includegraphics{images/keywords_counted.pdf}
\caption{The distribution of keywords per item in the Edoc sample data
set. The leftmost boxplot shows the distribution of cleaned keywords
(\(min = 0\), \(Q1 = 4\), \(M = 6\), \(Q3 = 8\), \(max = 87\)); the
other boxplots show the distribution of cleaned keywords with reconciled
QID (\(min = 0\), \(Q1 = 2\), \(M = 4\), \(Q3 = 6\), \(max = 80\)), MeSH
ID (\(min = Q1 = 0\), \(M = 2\), \(Q3 = 4\), \(max = 63\)), and YSO ID
(\(min = Q1 = 0\), \(M = 1\), \(Q3 = 2\), \(max = 46\)). All four
distributions are equally consistent, but there is a linear shrinkage of
the center leaving MeSH and YSO with potentially too few descriptors to
represent an adequate indexing.}
\end{figure}

@@

@@

Or put as question: what fraction of the subject terms suggested by
Annif are also in the native gold standard? The metric of precision is
implemented by \texttt{\_Analysis.get\_precision}.

@@

Put as question: what fraction of the subject terms in the gold standard
were suggested by Annif? The metric of recall is implemented by
\texttt{\_Analysis.get\_recall}.

@@

!! how to deal with items that have more than 10 keywords in standard??
just look at data in IQR?

@@

!! Clean up: rename
\texttt{/indexed/indexed\_master\_mesh\_enriched.json} to
\texttt{/indexed/master\_final.json} or something short.
